### 2024-11-14 conteudo/introduction/intro.tex
choose to put in appendix the list of gray
add appendix of gray lit
add arkanjo and change proposed tool to arkanjo in multiples places

Given the unsuccessful results of our search in the formal literature, we
turned to gray literature for solutions but were also met with limited success.
The best solutions we found in the gray literature were primitive, merely
identifying every pair of code files that are duplications. The code files in
the AMD Display driver containing duplicated code typically have specific code
unique to each file. Therefore, a solution that identifies duplication in a
deeper context is necessary to find accurate duplications within the Linux
kernel context.

@@

@@

This manuscript consists of five more chapters. Chapter \ref{cha:back} presents
the literature overview for code duplication detection (main definitions,
current approaches in the literature), a brief description of the Linux kernel,
and a review of refactoring methods used throughout this research. Chapter
\ref{cha:tool} presents our proposed tool to detect code duplication in the
Linux kernel, describing all the main components.  Chapter \ref{cha:method}
describes the research methods selected to guide our work. Chapter
\ref{cha:results} shows the first results obtained from the research methods to evaluate
our proposed tool and presents the current research stage and the work plan,
with the addition of a discussion about our preliminary results.

>>>>

Given the unsuccessful results of our search in the formal literature, we
turned to gray literature for solutions but were also met with limited success.
The best solutions we found in the gray literature were primitive, merely
identifying every pair of code files that are duplications. The code files in
the AMD Display driver containing duplicated code typically have specific code
unique to each file. Therefore, a solution that identifies duplication in a
deeper context is necessary to find accurate duplications within the Linux
kernel context. 
The list of gray literature tools examined in this exploratory research 
is available in Appendix A \ref{app:gray}.

@@

\label{sec:intresearch}

@@

This manuscript consists of five more chapters. Chapter \ref{cha:back} presents
the literature overview for code duplication detection (main definitions,
current approaches in the literature), a brief description of the Linux kernel,
and a review of refactoring methods used throughout this research. Chapter
\ref{cha:tool} presents Arkanjo, our proposed tool to detect code duplication in the
Linux kernel, describing all the main components.  Chapter \ref{cha:method}
describes the research methods selected to guide our work. Chapter
\ref{cha:results} shows the first results obtained from the research methods to evaluate
our tool and presents the current research stage and the work plan,
with the addition of a discussion about our preliminary results.

### 2024-11-14 conteudo/tool/functionalities.tex
add arkanjo and change proposed tool to arkanjo in multiples places

\begin{figure}
\includegraphics[scale=0.5]{explorer_example}
\caption{Example of the \textit{Duplication Explorer} functionality of the proposed tool in action.}
\label{fig:explorer_ex}
\end{figure}

@@

\begin{figure}
\includegraphics[scale=0.5]{function_example}
\caption{Example of the \textit{Function Information} functionality of the proposed tool in action.}
\label{fig:function_ex}
\end{figure}

@@

\begin{figure}
\includegraphics[scale=0.5]{relatory_example}
\caption{Example of the \textit{Duplication Report} functionality of the proposed tool in action.}
\label{fig:relatory_ex}
\end{figure}

>>>>

\begin{figure}
\includegraphics[scale=0.5]{explorer_example}
\caption{Example of the \textit{Duplication Explorer} functionality of the Arkanjo tool in action.}
\label{fig:explorer_ex}
\end{figure}

@@

\begin{figure}
\includegraphics[scale=0.5]{function_example}
\caption{Example of the \textit{Function Information} functionality of the Arkanjo tool in action.}
\label{fig:function_ex}
\end{figure}

@@

\begin{figure}
\includegraphics[scale=0.5]{relatory_example}
\caption{Example of the \textit{Duplication Report} functionality of the Arkanjo tool in action.}
\label{fig:relatory_ex}
\end{figure}
